---
title: "User Modelling, plots"
author: Remon
date: 21/10/2024
output: rmarkdown::html_vignette
---

Packages:

```{r echo = T, results = 'hide'}
library(tidyverse)
library(reshape2)
library(ggsignif)
library(cowplot)
```

load data

```{r echo = T, results = 'hide'}
path <-  ".//Participant Data Final//"
trialdata <- list.files(path = path, pattern = "subj_.*\\.csv$", full.names = TRUE) %>%
    map_df(~ {
        # Extract the subject number from the filename
        filename <- basename(.)
        subj_number <- as.integer(str_extract(filename, pattern ="\\d+")) # string to int
        # Read the CSV file and add the subject number as a new column
        read_csv(., show_col_types = FALSE) %>%
            mutate(subj_nr = subj_number)
    })
trialdata$image_set <- factor(trialdata$image_set)

demodata <-
    list.files(path = path, pattern = "demo_.*\\.csv$", full.names = TRUE) %>%
    map_df(~read_csv(., show_col_types = FALSE))

```

omit rows with reregistering of first trial of model (bug)

```{r}
trialdata <- trialdata %>% filter(start_time != 0)
```

Incorporate demo data into trialdata df

```{r}
data <- trialdata %>% mutate(model_firstBlock = ifelse(experiment_order == 0 | experiment_order == 2, "Standard", "Doubt-Detection")) %>%
  left_join(demodata,by = 'subj_nr')

data$doubt_classificationCNN <- as.factor(data$doubt_classificationCNN)
data$subj_nr <- as.factor(data$subj_nr)
data$model_type <- as.factor(data$model_type)
data$doubt <- as.factor(data$doubt)
data$doubt_classificationCNN <- as.factor(data$doubt_classificationCNN)
```

```{r}
block1data <- data %>% filter(block_n ==1)
experimentdata <- data %>% filter(block_n !=1)
```

delete first presentation per answer, per person. This for plotting purposes only, prob shouldnt do this for the analysis

```{r}
rows_before <-  nrow(experimentdata)
experimentdata <- experimentdata %>%
  group_by(subj_nr,answer) %>% slice(-1) %>% ungroup()

rows_after <-  nrow(experimentdata)
print(paste(rows_before-rows_after, "rows deleted"))
```

basic plots for percentage correct grouped by manipulation

```{r}
correctRatio_model <- experimentdata %>%
  group_by(model_type) %>%
  summarize(correct = sum(correct == 1),
            n = n())
correctRatio_imageSet <- experimentdata %>%
  group_by(image_set) %>%
  summarize(correct = sum(correct == 1),
            n = n())

correctRatio_modelXimage <- experimentdata %>%
  group_by(model_type,image_set) %>%
  summarize(correct = sum(correct == 1),
            n = n()) %>%
  unite("model_image", model_type, image_set, sep = "_")

correctRatio_order <- experimentdata %>%
  group_by(model_type, model_firstBlock) %>%
  summarize(correct = sum(correct == 1),
            n = n()) %>%
  unite("firstmodel_model", model_type, model_firstBlock, sep = "_")

correct_bygrouping_list <- list(correctRatio_model, correctRatio_imageSet, correctRatio_modelXimage, correctRatio_order)
legend_list <-  list(
  c('Doubt-Detection', 'Standard'),
  c('Image Set 1', 'Image Set 2'),
  c('Doubt-Detection x Set 1', 'Doubt-Detection x Set 2', 'Standard x Set 1' ,'Standard x Set 2'),
  c('Doubt-Detection if DD first block', 'Standard if DD first block', 'Doubt-Detection if Standard first block', 'Standard if Standard first block')
)

correct_plot_list <- list()

# Now plot
for (i in 1:length(correct_bygrouping_list)) {
  category <-  correct_bygrouping_list[[i]]
  legend <-  legend_list[[i]]
  grouping <- sym(colnames(category)[1])
  plot <- category %>%
  ggplot(aes(x = !!grouping, y = correct/n * 100)) + geom_bar(stat = "identity", aes(fill = !!grouping)) +
  xlab("") +
  ylab("Percentage Correct")+
  ggtitle("percentage correct by grouping") +
  scale_fill_discrete(labels = legend) +
  theme_classic() +
    theme(axis.text.x=element_blank())+
    theme(legend.title=element_blank()) +
        geom_text(aes(label = paste0(round(correct/n * 100, 1), "%")),
            position = position_stack(vjust = 1),  # Position labels above bars
            vjust = -0.1,
            color = "black")

  correct_plot_list[[grouping]] <- plot
}

plot_grid(plotlist= correct_plot_list)

```

percentage correct per country

```{r}
#prop.table(table(experimentdata$answer, experimentdata$correct),1)*100

percCorrect_country <- experimentdata %>%
  group_by(answer) %>%
  summarize(correct = sum(correct == 1),
            n = n())

country_plot <- percCorrect_country %>%
  ggplot(aes(x = answer, y = correct/n * 100)) +
  geom_bar(width=0.4, position = position_dodge(width=0.5),stat = "identity", aes(fill = answer)) +
  xlab("") +
  ylab("Percentage Correct") +
  scale_fill_discrete(guide="none") +
  theme_classic() +
        geom_text(aes(label = paste0(round(correct/n * 100, 1), "%")),
            position = position_stack(vjust = 1),  # Position labels above bars
            vjust = -0.1,
            color = "black")

country_plot
```

often seen corrections

```{r}
experimentdata <- experimentdata %>%
  group_by(answer) %>%
  mutate(perc_correct = sum(correct == 1)/n()) %>% ungroup()

corrections <- experimentdata %>%
  filter(perc_correct < 0.7) %>%
  group_by(answer,user_answer) %>%
  summarize(
    count = n(), .groups = 'drop') %>%
  group_by(answer) %>%
  mutate(total_count = sum(count))

countries_below70 <-  unique(corrections$answer)

country_plot_list <-  list()
for (i in countries_below70) {
  country <-  corrections %>% filter(answer == i)
  plot <- country %>%
        ggplot(aes(x=user_answer, y = count/total_count * 100)) +
        geom_bar(stat = "identity", aes(fill = user_answer)) +
        ggtitle(paste(i, "and it's transcriptions")) +
        xlab("") +
        ylab("Percentage") +
        scale_fill_discrete(guide="none")  +
        theme_classic()+
        theme(plot.title = element_text(size=15)) +
        geom_text(aes(label = paste0(round(count / total_count * 100, 1), "%")),
            position = position_stack(vjust = 1),  # Position labels above bars
            vjust = -0.1,
            color = "black")

  country_plot_list[[i]] <- plot

}

plot_grid(plotlist=country_plot_list)


```

```{r}
# should probably change this to alpha per person
Alpha_country <- experimentdata %>%
  group_by(answer, model_type) %>%
  slice_tail(n=1) %>%
  summarize(alpha = mean(alpha))
Alpha_country <- Alpha_country %>%
  group_by(model_type) %>%
  mutate(mean_alpha = mean(alpha))



Alpha_plot <- Alpha_country %>%
  ggplot(aes(x = answer, y = alpha)) +
  geom_bar(width=0.4, position = position_dodge(width=0.5),stat = "identity", aes(fill = model_type)) +
  geom_line(aes(y= mean_alpha, group = model_type, colour = model_type), linetype = "dashed") +
  xlab("") +
  ylab("Alpha") +
  #scale_fill_discrete(guide="none") +
  theme_classic()

Alpha_plot
```

check percentage correct CNN classification

```{r}
propCorrectCNN <- prop.table(table(block1data$doubt, block1data$doubt_classificationCNN),1)*100

rownames(propCorrectCNN) <- c('Confident_byUser', 'Doubtful_byUser')

propCorrectCNN_pp <- block1data %>% 
  drop_na(doubt) %>% 
  group_by(subj_nr,doubt, doubt_classificationCNN, .drop = FALSE) %>% 
  summarise(n = n()) %>%
  mutate(freq = n / sum(n)) %>% 
  replace(is.na(.), 0)
```

check percentage correct after error for both systems

```{r}
experimentdata <- experimentdata %>%
  group_by(answer) %>% 
  mutate(correct_after_error = factor(ifelse(correct == TRUE & lag(correct) == FALSE, TRUE , ifelse(correct == FALSE & lag(correct) == FALSE, FALSE, NA)))) %>% ungroup()

correct_after_error_perc <- prop.table(table(experimentdata$correct_after_error, experimentdata$model_type),2)*100 # correct after error

rownames(correct_after_error_perc) <- c('Error_after_error', 'Correct_after_error'); correct_after_error_perc

correct_after_error_pp <- experimentdata %>% 
  drop_na(correct_after_error) %>% 
  group_by(subj_nr, model_type, correct_after_error, .drop = FALSE) %>% 
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))

correct_after_error_doubt <- experimentdata %>% 
  drop_na(correct_after_error) %>% 
  group_by(model_type, doubt_classificationCNN, correct_after_error) %>% 
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))
```

correct after correct

```{r}
experimentdata <- experimentdata %>%
  group_by(answer) %>% 
  mutate(correct_after_correct = factor(ifelse(correct == TRUE & lag(correct) == TRUE, TRUE , ifelse(correct == FALSE & lag(correct) == TRUE, FALSE, NA)))) %>% ungroup()

correct_after_correct_perc <- prop.table(table(experimentdata$correct_after_correct, experimentdata$model_type),2)*100 # correct after error

#rownames(correct_after_correct_perc) <- c('Error_after_correct', 'Correct_after_correct'); correct_after_correct_perc

correct_after_correct_pp <- experimentdata %>% 
  drop_na(correct_after_correct) %>% 
  group_by(subj_nr, model_type, correct_after_correct, .drop = FALSE) %>% 
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))

correct_after_correct_doubt <- experimentdata %>% 
  drop_na(correct_after_correct) %>% 
  group_by(model_type, doubt_classificationCNN, correct_after_correct) %>% 
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))
```

correct after error-correct

```{r}
experimentdata <- experimentdata %>%
  group_by(answer) %>% 
  mutate(correct_after_errcor = factor(ifelse(correct == TRUE & lag(correct_after_error) == TRUE, TRUE , ifelse(correct == FALSE & lag(correct_after_error) == TRUE, FALSE, NA)))) %>% ungroup()

correct_after_errcor_perc <- prop.table(table(experimentdata$correct_after_errcor, experimentdata$model_type),2)*100 # correct after error

rownames(correct_after_errcor_perc) <- c('Correct_after_ErrCor', 'Error_after_ErrCor'); correct_after_errcor_perc

correct_after_errcor_pp <- experimentdata %>% 
  drop_na(correct_after_errcor) %>% 
  group_by(subj_nr, model_type, correct_after_errcor, .drop = FALSE) %>% 
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))

correct_after_errcor_doubt <- experimentdata %>% 
  drop_na(correct_after_errcor) %>% 
  group_by(model_type, doubt_classificationCNN, correct_after_errcor) %>% 
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))
```
